A Formalisation of Sturm's Theorem\\in Isabelle/HOL

### 2013-12-18 slides/slides.tex
Tuned slides

\begin{frame}{Motivation}
\begin{description}
\item[We have:] a polynomial with real coefficients
\pause\item[We want:] the number of real roots in a specific interval
\end{description}
\end{frame}

\begin{frame}{Motivation}
\vspace*{1.65mm}
\begin{description}
\item[We have:] a polynomial with $\overbrace{\text{\color{red}real\ coefficients}}^{\text{not\ really}}$
\vspace*{-0.05mm}
\item[We want:] the number of real roots in a specific interval
\end{description}
\vspace{5mm}
\pause
For \enquote{real} computations: restricted to appropriate subset of $\RR$, such as $\QQ$.
\end{frame}

@@

\begin{frame}{Notation}
\emph{Sign changes:} $\sigma(P_0,\ldots,P_{n-1}; x)$ denotes denotes the number of sign changes in the sequence $P_0(x), \ldots, P_{n-1}(x)$\\[2mm]
For the functionally inclined:\vskip-6mm
$$\sigma(ps; x) = (\mathrm{length} \circ \mathrm{remdups\_adj} \circ \mathrm{filter}\ (\neq 0) \circ \mathrm{map}\ (\lambda p.\ p(x)))\ ps\ -\ 1$$
\end{frame}

>>>>

\begin{frame}{Motivation}
\begin{description}
\item[We have:] a polynomial with {\text{\only<1,2>{real coefficients}\only<3->{\color{red}real coefficients}}}
\pause\item[We want:] the number of real roots in a specific interval
\end{description}\vskip5mm
\pause
For reals?\\\pause
No. Only for rationals. (or any other sufficiently nice subset of $\RR$)
\end{frame}

@@

\begin{frame}{Notation}
\emph{Sign changes:} $\sigma(P_0,\ldots,P_{n-1}; x)$ denotes the number of sign changes in the sequence $P_0(x), \ldots, P_{n-1}(x)$\\[2mm]
For the functionally inclined:\vskip-6mm
$$\sigma(ps; x) = (\mathrm{length} \circ \mathrm{remdups\_adj} \circ \mathrm{filter}\ (\neq 0) \circ \mathrm{map}\ (\lambda p.\ p(x)))\ ps\ -\ 1$$
\end{frame}
